User-level Grid Monitoring with Inca 2

### 2007-02-21 papers/hpdc-gmw-2007/paper.tex
small mods to arch figure and added arch intro
git-svn-id: file:///localdisk/subversion/inca/trunk/pubs@6533 7dba3f4a-8be6-0310-8b3b-b4fec25ea7f3

\documentclass[times, 10pt,twocolumn]{article} 
\usepackage{epsfig}
\usepackage{latex8}
\usepackage{times}
\usepackage{url}

@@

% Standard "Grids are good" intro paragraph.  But are complex.  
Grid systems provide unified and coherent access to distributed computing,
data storage and analysis, instruments, and other resources.  These systems
require the careful coordination of software packages, services, and
configurations across multiple, heterogenous resources.  The TeraGrid
project~\cite{teragrid}, for example, manages the coordination of software and
services by deploying and monitoring a common user environment across
distributed, heterogeneous resources. The organization of TeraGrid software
and services is referred to as the Common TeraGrid Software and Services
(CTSS).  TeraGrid's software and services uniformity simplifies access to its
resources, which consist of more than 102 teraflops of compute capability and
more than 15 petabytes of online storage, all interconnected by a network that
can transfer a terabyte of data in under 10 minutes.

% Complex means they are difficult to provide and maintain. Describe the
% stakeholders.   Monitoring is needed.
Providing and maintaining a stable infrastructure for these complex 
Grid systems poses challenges for both administrators who build and
maintain Grid resources and scientists who use them.  First, system
administration is distributed across multiple administrative domains which
requires a significant amount of coordination.  This is typically performed by
a group of Grid operators who take into account local site policies 
and decide when software (including updates and patches) should be deployed to
resources and how it should be configured for the set of heterogenous
resources.  Each site's system administrators, who are oftentimes not Grid
experts, are then responsible for providing the required Grid software
components and services for their resource and debugging any problems that
arise.  Well-defined requirements and good communication are required in this
model.  Otherwise inconsistencies between the resources arise that can either
inconvenience the user or prevent them from using particular resources
together.  Second, as a large distributed system, failures will occur over
time in the Grid services due to network or system failures, software
misconfiguration, or software bugs.  In order to detect such problems, 
monitoring of the resources is required.

@@

% What user-level monitoring provides and why we think it is good
User-level Grid monitoring approaches testing and performance measurement of
the Grid infrastructure from the user perspective.  The goal is to act as an
impartial test user of the Grid and detect problems with the Grid
infrastructure so they can be fixed before users notice them -- user
complaints should not be the first indication of Grid failures.  User-level
Grid monitoring has the following characteristics:

@@

\item Tests or performance measurements of the Grid infrastructure should be
done from a standard user account.  Tests executed by system administrators may
not reflect regular user experiences because they run under privileged
accounts that often have custom shell initialization files.
System administrators may also configure tests using undocumented information
(e.g., they know GridFTP server hostnames not in the user guide).

\item Because the Grid infrastructure is dynamic, Tests or performance
measurements should be executed periodically and automated.

\item A user GSI credential should be issued and
used by the monitoring system to test services that require authentication.

\item Tests should be executed locally on all Grid resources when appropriate
so that all Grid access points available to users are tested.

\item Also important to test some services from site to site.
\end{itemize}
Amount of testing can vary and is oftentimes limited by the amount of
reosurces that can be addressed to it.  A good approach is to test all the
commands that exist in the user documentation or have at least one basic test
for each software component of the Grid infrastructure.  
commands that users use and tests to see if they operate as expected. Execute
commands published in user
documentation, detect problems otherwise reported by users.

so called user-level Grid monitoring is bIn our view, what was
needed was a separate
monitoring system to perform automated, periodic user-level Grid testing with
the following features:
User-level Grid monitoring is x and is valuable.  
At that
time, the only available user-level Grid monitoring tools were the NCSA
TestGrid script [9] and GITS [10], scripts that run a fixed number of Grid
tests and output results in HTML.  Although these tools were easy to install
and produced useful information, they showed only the view of the Grid from a
single resource, lacked automation, and were not easily extensible.

% Inca 1~\cite{inca1} first addressed user-level Grid monitoring but had
% limitations.  We learned lessons from our TeraGrid deployment.  
In 2003, SDSC, in partnership with TeraGrid, began developing the Inca
monitoring tool to implement a user-level monitoring system with the above
features and started using it to validate and verify that CTSS was deployed
consistently across all TeraGrid resources and to monitor its status.  
The initial version of Inca was implemented as a client-server architecture.
It provided data collection, data storage (with limited archiving
capabilities) that was accessible from a Web services interface, and data
display though Web status pages.  Inca was first deployed to TeraGrid in mid
2003 and released in late 2003. After running Inca 1 for a year and a half on
TeraGrid, we learned some valuable lessons and designed Inca version 2, our
current release.  Inca 2 contains a number of substantial improvements over
Inca 1 with respect to security, installation and maintenance, and storage
capabilities.  A pre-release of Inca 2 was provided in February 2006 and a
beta release in November 2006.  A production version of Inca 2 was released in
January 2007.  Currently, seven other Grids in the U.S., Europe, and Australia
use Inca.

% This motivated our development of a new version of Inca.
In the next section, we describe our experiences with deploying Inca 1 to
TeraGrid and the lessons learned.  We then describe the Inca 2 architecture
and the benefits it provides.  Use cases illustrate that Inca 2 is being used
today and has great results.

\Section{Features}

% Philosophy of user-level testing
% Practical byproducts

@@

%------------------------------------------------------------------------- 
%------------------------------------------------------------------------- 
\Section{Architecture}

\SubSection{Overview}
% may not need to leave in here -- intro is assumed to be overview
% Overview of all architecture components -- arch picture
% move text to here I think
1) The user creates a suite using incat and submits it to the agent

2) The agent 
    a) fetches reporters from the reporter repository
    b) creates a reporter manager on each resource
    c) sends the suite and reporters to each reporter manager.

3) Each reporter manager executes reporters according to its schedule and
sends results (reports) to the depot

4) Data consumers display collected data (reports) by querying the depot

\begin{figure*}[Htb]
  \centering
  \mbox{\epsfig{file=arch.eps, width=.8\textwidth}}
  \caption{\label{arch_fig} Inca architecture.}
\end{figure*}

>>>>

\documentclass[times,10pt,twocolumn]{article} 
\usepackage{epsfig}
\usepackage{latex8}
\usepackage{times}
\usepackage{url}

@@

% Standard "Grids are good" intro paragraph.  But are complex.  
Grid systems provide unified and coherent access to distributed computing,
data storage and analysis, instruments, and other resources.  These systems
require the careful coordination of software packages, services, and
configurations across multiple, heterogeneous resources.  The TeraGrid
project~\cite{teragrid}, for example, manages the coordination of software and
services by deploying and monitoring a common user environment across
distributed, heterogeneous resources. The organization of TeraGrid software
and services is referred to as the Common TeraGrid Software and Services
(CTSS).  TeraGrid's software and services uniformity simplifies access to its
resources, which consist of more than 102 teraflops of compute capability and
more than 15 petabytes of online storage, all interconnected by a network that
can transfer a terabyte of data in under 10 minutes.

% Complex means they are difficult to provide and maintain. Describe the
% stakeholders.   Monitoring is needed.
Providing and maintaining a stable infrastructure for these complex 
Grid systems poses challenges for both administrators who build and
maintain Grid resources and scientists who use them.  First, system
administration is distributed across multiple administrative domains which
requires a significant amount of coordination.  This is typically performed by
a group of Grid operators who take into account local site policies 
and decide when software (including updates and patches) should be deployed to
resources and how it should be configured for the set of heterogeneous
resources.  Each site's system administrators, who are oftentimes not Grid
experts, are then responsible for providing the required Grid software
components and services for their resource and debugging any problems that
arise.  Well-defined requirements and good communication are required in this
model.  Otherwise inconsistencies between the resources arise that can either
inconvenience the user or prevent them from using particular resources
together.  Second, as a large distributed system, failures will occur over
time in the Grid services due to network or system failures, software
misconfiguration, or software bugs.  In order to detect such problems, 
monitoring of the resources is required.

@@

% What user-level monitoring provides and why we think it is good
User-level Grid monitoring approaches testing and performance measurement of
the Grid infrastructure from the user perspective.  The goal is to act as an
impartial test user of the Grid and detect problems with the infrastructure so
they can be fixed before users notice them -- user complaints should not be
the first indication of Grid failures.  We refer to an executable program that
tests or measures some aspect of a system or installed software from the
user-perspective as a reporter.  User-level Grid monitoring has the following
characteristics:

@@

\item In order to reflect regular user experiences, tests or performance
measurements of the Grid infrastructure should be done from a standard user
account.  In fact, it is important to not execute under a system
administrator's account because they may be privileged and often have custom
shell initialization files.

\item Also in order to reflect regular user experiences, tests should be
written and configured using information directly from user documentation
(e.g., hostnames, ports, pathnames, etc.).  This may not always be possible
when documentation and testing are done in parallel in a pre-production
environment but they should be closely coordinated activities.

\item Since Grids are dynamic, user-level tests or performance measurements
should be automated and executed periodically.

\item Tests or performance measurements that interact with Grid services
require authentication and should be executed using a standard user GSI
credential that is mapped to the standard user account.

\item Tests or performance measurements should be executed locally on all Grid
resources when appropriate so that all Grid access points available to users
are verified.  Similarly, it is important to execute some tests all-to-all
in order to detect site-to-site configuration errors such as authentication
problems.

\end{itemize}

\noindent In our experience, writing and maintaining user-level tests and
performance measurements is an iterative refinement process since Grids are
dynamic and the software environment changes over time as packages are
upgraded.  It is also difficult to write and deploy a test perfectly the first
time because of portability issues and sometimes incomplete user
documentation.  For example, it may take a few iterations to determine whether
detected failures are the result of a faulty test, fault user documentation,
or a faulty system.  Realistically, this is a labor-intensive activity and
thus the amount of user-level Grid monitoring is often limited by the amount
of people resources that can be assigned to it.  However, A good goal is to
test all the commands that exist in the user documentation and/or have at
least one basic test for each software component of the Grid infrastructure.

% Inca 1~\cite{inca1} first addressed user-level Grid monitoring but had
% limitations.  We learned lessons from our TeraGrid deployment and
% developed Inca 2.
In 2003, SDSC, in partnership with TeraGrid, began developing Inca
1~\cite{inca1} to implement a user-level monitoring system with the above
features and started using it to validate and
verify that CTSS was deployed consistently across all TeraGrid resources and
to monitor its status.  At that time, the only available user-level Grid
monitoring tools were the NCSA TestGrid script~\cite{ncsa-test} and
GITS~\cite{gits}, scripts that run a fixed number of Grid tests and output
results in HTML.  Although these tools were easy to install and produced
useful information, they showed only the view of the Grid from a single
resource, lacked automation, and were not easily extensible.  The initial
version of Inca was implemented as a client-server architecture.  It provided
data collection, data storage (with limited archiving capabilities) that was
accessible from a Web services interface, and data display though Web status
pages.  Inca was first deployed to TeraGrid in mid 2003 and released in late
2003. After running Inca 1 for a year and a half on TeraGrid, we learned some
valuable lessons and designed Inca 2, our current release.  Inca 2
contains a number of substantial improvements over Inca 1 with respect to
security, installation and maintenance, and storage capabilities.  A
production release of Inca 2 was provided in February 2007 and has been
running on TeraGrid since November 2006.  Currently, seven other Grids in the
U.S., Europe, and Australia use Inca.

% This motivated our development of a new version of Inca.
In the next section, we describe the features of Inca 2 and note which
are new features based on our experiences with deploying Inca 1 on TeraGrid.
We then describe the Inca 2 architecture and how it can be used to provide
user-level Grid monitoring.  In Section~\ref{usecases}, we describe two 
uses of Inca 2 for Grid software environment verification and benchmarking.  
Finally, we describe some future work and summarize the paper.

%------------------------------------------------------------------------- 
\Section{Inca 2 Features}

% Philosophy of user-level testing
% Practical byproducts
The goal of the Inca 2 design was to

@@

%------------------------------------------------------------------------- 
\Section{Architecture}

\begin{figure*}[htb]
  \centering
  \mbox{\epsfig{file=arch.eps, width=.8\textwidth}}
  \caption{\label{arch_fig} Inca architecture.}
\end{figure*}

% overview description of components
Figure~\ref{arch_fig} shows the architecture of Inca 2 designed to implement
the features described in the previous section.  Inca 2 is composed of 3 core
components (in highlighted box):  the agent, depot, and reporter manager.
The \textit{agent} and \textit{reporter managers} coordinate the execution of
tests and performance measurements on the Grid resources and the
\textit{depot} stores and archives the results.  The inputs to Inca 2 are one
or more \textit{reporter repositories} that contain user-level tests and
benchmarks called \textit{reporters} and a configuration file describing how
to execute them on the Grid resources created using an administration GUI tool
called \textit{incat} (Inca Administration Tool).  The output or results
collected from the resources are queried by the \textit{data consumer} and
displayed to users.  The following steps describe how an Inca administrator
would deploy user-level test and/or performance measurements to their
resources.

\begin{enumerate}
\item The Inca administrator creates a deployment configuration file using
incat and submits it to the agent.

\item The agent
  \begin{enumerate}
    \item fetches reporters from the reporter repository
    \item creates a reporter manager on each resource
    \item sends the reporters and instruction for executed them to each reporter manager.
  \end{enumerate}

\item Each reporter manager executes reporters according to its schedule and
sends results (reports) to the depot

\item Data consumers display collected data (reports) by querying the depot
\end{enumerate}

\noindent The following subsections describe the Inca components in more
detail in the order of the steps above.
